Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-06 paper.qmd
Updated langevitour for Five Gau clusters

df_model_data_n <- bind_rows(data_gau, df_b)

@@

## Compute hexbin parameters
num_bins_x_gau1 <- 25
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

@@

distance_df_small_edges_gau1 <- distance_gau1 |>
  filter(distance < benchmark_gau1) |>
  mutate(ID = row_number()) #|>
  #filter(!(ID %in% c(97)))

>>>>

df_model_data_n <- bind_rows(df_b, data_gau)

@@

## Compute hexbin parameters
num_bins_x_gau1 <- 20
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

@@

distance_df_small_edges_gau1 <- distance_gau1 |>
  filter(distance < benchmark_gau1) #|>
  #mutate(ID = row_number()) #|>
  #filter(!(ID %in% c(97)))
